% updated April 2002 by Antje Endemann
% Based on CVPR 07 and LNCS, with modifications by DAF, AZ and elle, 2008 and AA, 2010, and CC, 2011; TT, 2014; AAS, 2016; AAS, 2020

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{comment}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{color}

% INITIAL SUBMISSION - The following two lines are NOT commented
% CAMERA READY - Comment OUT the following two lines
\usepackage{ruler}
\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}



\begin{document}
% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
% \linenumbers
\pagestyle{headings}
\mainmatter

\def\ECCVSubNumber{3290}  % Insert your submission number here

\title{3D Reconstruction of Clothes using a Human Body Model and its Application to Image-based VTON} % Replace with your title

% INITIAL SUBMISSION 
%\begin{comment}
\titlerunning{ECCV-20 submission ID \ECCVSubNumber} 
\authorrunning{ECCV-20 submission ID \ECCVSubNumber} 
\author{Anonymous ECCV submission}
\institute{Paper ID \ECCVSubNumber}
%\end{comment}
%******************

% CAMERA READY SUBMISSION
\begin{comment}
\titlerunning{3D Reconstruction of Clothes ... VTON}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Matiur Rahman Minar\inst{1}\orcidID{0000-0002-3128-2915} \and
Thai Thanh Tuan\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Heejune Ahn\inst{3}\orcidID{2222--3333-4444-5555}  \and
Paul Rosin\inst{3}\orcidID{2222--3333-4444-5555}   \and
Yukun Lai\inst{3}\orcidID{2222--3333-4444-5555}  }
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Seoul National University of Science and Technology, Seoul  08544, South Korea \and
Cardiff University, Cardiff, 69121 Heidelberg, UK
\email{heejune@seoultech.ac.kr}\\
\url{http://www.springer.com/gp/computer-science/lncs}}
\end{comment}
%******************
\maketitle

\begin{abstract}

Image-based virtual try-on (VTON) has drawn increasing attraction for online apparel shopping, mainly because of not requiring 3D information of try-on clothes and target humans. However, the existing 2D algorithms, even utilizing the advanced non-rigid deformation algorithm, can not handle the 3D shape changes for the postures of target humans. In this study, we propose the 3D cloth reconstruction method using 3D human body model. The 3D model of try-on cloth can be more easily deformed when applied to the rest posed standards human model. Thereafter the pose and shape of cloth can be transferred to the ones of the target humans estimated from a 2D image. Finally, the deformed cloth model can be rendered and blended together with unchanged cloth and human parts. The experimental results with an open dataset shows the reconstructed cloth shapes are significantly more natural compared to the 2D imaged based deformation results, when the human pose and shape are estimated accurately.         

\keywords{3D Model, SMPL, 3D Reconstruction, Cloth deformation, Virtual Try-on}
\end{abstract}


\include{sec1}  % intro
\include{sec2}  % performance evaluation
\include{sec3}  % 3D reconstruction
\include{sec4}  % cloth transfer


\section{Conclusions}  \label{section:conclusion}

In this paper, we proposed 3D cloth model reconstruction method using single cloth image. Leveraging the 3D body model, we can make it easy to reconstruct 3D shape information. The 3D cloth model is used for transferring the cloth to target human model.  The transferred clothes can be integrated with the human image contents for realizing the pose and shape changes which can not be realizable by existing image based VTON methods.

However, the algorithms in each step of the pipeline are not perfect and have many things to improve at present. Especially the in-accuracy in estimating human pose and shape makes the integrated VTON results not natural enough. Therefore, we can consider to improve the SMPLify\cite{Bogo2016SMPLify} algorithm or use different blending step that suits for the 3D model input.
     

  
\clearpage
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{egbib}



\end{document}
